Text Is All You Need

### 2023-05-11 docs/hes_final/presentation.qmd
Transformer Slide Tweaks

- Trained using a dataset that drew multiple samples per country per month of 50 articles each 
- The same label was used for each subsample, creating multiple unique training examples for each country and month 
- This produced a larger, but more distorted corpus
:::

@@

### Training the Classifier

@@

::: {.column width="50%"}
- Once the Encoder was trained, it's penultimate layer of 16 dense neurons was exposed and the model was frozen
- Each country/month matrix was then fed into in batches of 50 articles, yeilding a single training example for each country and month of size $16\times\frac{n}{50}$

>>>>

- Trained using a dataset that drew multiple samples per country per month of 50 articles each 
- This created multiple unique training examples for each country and month 
- Once trained, the Encoder's weights were frozen and penultimate layer was exposed
:::

@@

### The Classifier

@@

::: {.column width="50%"}
- Each country/month embedding matrix was passed into the Encoder in batches of 50 articles
- This produced a single distilled training example for each country and month
- This final, undistorted data set was then used for classification
